---
title: "ATEP Assignment 1"
subtitle: "Comparing Original and Media Reports"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
header-includes:
  - \usepackage[table]{xcolor}
  - \definecolor{stripe}{RGB}{237,250,255}
  - \renewcommand{\familydefault}{\sfdefault}
  - \renewcommand{\baselinestretch}{1.2} 
  - \setlength\extrarowheight{2pt}
---

```{r, echo = FALSE}
ind_fb <- dplyr::filter(marking$marks, id == myid)
```


### Student ID: `r as.character(myid)`

Feedback provided by `r ind_fb$marker`

*Note on feedback*: You should find it helpful to consider the comments made here when it comes to writing the reports for the next assessment, in terms of the strengths of your skills and areas that could be further developed.  In order to obtain the most out of this feedback, you should read through your coursework again.

The aim of this assignment is to develop your comprehension and critical analysis of both primary (original research) and secondary (media reports)  literature in the field of evolutionary psychology.

## Preliminary mark: `r ind_fb$mark`


```{r category-table, echo = FALSE, results='asis'}

cats <- c("Doing really well", 
          "Going well, but build your skills", 
          "You need to do more work here")

category_table(ind_fb, marking$eval, cats)
  
```


## What you could focus on in future work

### What to keep doing

`r ind_fb$strengths`

### Key things to address

`r ind_fb$weaknesses`

### Generic Feedback

```{r Q1, echo = FALSE, results='asis'}
if (ind_fb$question == "Q1") {
  cat("

## Question text: The question can be written this way.

* Bullet point 1
* Bullet Point 2

Some answered this question by looking at the influence of both genes and environment but forgot to address the element of their ‘dynamic interaction’ and to consider the implications for provision of this interaction – really important that you read the question very carefully and address all aspects in your answer.  Also remember the importance of balancing breadth and depth, some answers (possibly an attempt to demonstrate your reading) had a tendency to give long lists of studies.  Knowing the information is one thing – more important is to use that information effectively. Strong answers to this question showed extensive engagement in the literature but also used this knowledge effectively in constructing clear arguments in response to the question posed. 

Feed forward advice:

1. Make sure you answer the question asked!
2. Take time to structure answers.
3. Don’t just list/describe studies – discuss them

")
}
```

```{r Q2, echo = FALSE, results='asis'}
if (ind_fb$question == "Q2") {
  cat("Question for Q2\n\n")
  
  cat("Generic feedback for Q2")
}
```
